%=====================导=======言==============================
\documentclass[a4paper,11pt]{article}
%======================Include Packages========================

\usepackage[36428]{MCMthesis}  %队号在这里填写
%\usepackage[175,nosheet]{MCMthesis}%这个参数形式可去掉summary sheet首页。
\problem{A}  %选题
%===============设置正文和数学字体=============================
%有些字体需要安装一些字体文件，注意辨别。
%我参照 MCM论文集的字体 使用如下宏包来定制字体。
\usepackage{palatino}
\usepackage{longtable}
\usepackage{rotating}
\usepackage{threeparttable}
\usepackage{url}
%设置段落之间的距离，若不需要删除或者注释掉即可。
\setlength\parskip{.5\baselineskip}

%\def\abstractname{Summary}%可修改摘要名称

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%$$$$$$$==正文开始==$$$$$$$%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%==========================论文标题===============================
%A bright and subtle title.
\title{Fight against the Azrael: A optimized plan to eradicate Ebola}
\author{Team \#36428}  
\date{\today}
%=================================================================
%==================================================================
\begin{document}
\bibliographystyle{unsrt}   
%摘要需要放在maketitle之前才能保证运行正常
%====================摘=======要===================================
\def\abstractname{Abstract}%可修改摘要名称
\begin{abstract}
%注意600字
  The Ebola virus disease(EVD) is a lethal disease for humans and other primates caused by the deadly Ebola virus. It always attacks us with intense symptoms including fever, muscle pain, vomiting, rush or even death. What is more terrible is that at present, there does not exist any specific panacea to help us fight against EVD. According to the WHO long-term trace, the fatality rate of Ebola is up to 85\%, just second to the well-known lupomania. \\
  Fortunately, in this competition, we have been set in a background with the invention of new medication which could stop Ebola dispersal and cure patients with early symptoms. \\
  Our mission is to establish a model to numerically describe both the dispersal process of the lethal infection, and human being's process to manufacture, deliver and treat Ebola with this medicine. In order to implement such subtle and exciting procedures to fight against the Azrael, our team deliberately divide the procedures into two major steps: modelling the Ebola virus' basic spread progress in ideal cases at a particular region; modelling human being's hygiene actions and medicine delivery process, incorporating our fighting model into the virus' instinct properties and evaluating the results.\\
  In the first model, we modify the classical \textbf{S}usceptible, \textbf{I}nfective, \textbf{R}emoval(\textbf{SIR}) model in epidemic dynamic fields into our \textbf{SID}eath model. The \textbf{SID} model is meant to help us observing the disastrous infection process of Ebola in none human interference conditions. With the default attributes settings, we successfully generate a real-time simulation result of the spread and attacking process in Western Africa districts. \\
  In the second model, we expand the \textbf{SID} model to a brand-new one:  \textbf{S}usceptible, \textbf{P}rimary, \textbf{A}dvanced, \textbf{R}ecovery, \textbf{D}eath(\textbf{SPARD}). All parameters in \textbf{SPARD} are dynamic changing, which means a much more precise and subtle system. In addition, we develop a \textbf{E}arly \textbf{W}arning \textbf{S}ystem(EWS) to help doctors monitoring and determining the demand of medicine in real-time.
\begin{keywords}
Ebola, SIR, SPARD, Early Warning, Graph Optimization 
\end{keywords}
\end{abstract}

\maketitle
\pagestyle{empty}
%
\newpage                                                          %
%==================================================================


%====================生=成=目=录===================================
\tableofcontents                                                  %                                            %
\newpage
\pagestyle{fancy}                                                     %
%==================================================================
\input{body.tex}


\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%===========THE END OF PAPER============%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
